16s taxa stacked bar plot

### 2021-02-22 scripts/49_16s_stacked_barplot.Rmd
first time to work on the bars of the 16s

counts_data %>% 
  distinct(sampleid)

dat <- counts_data %>% 
  select(asv_key:count_total, count_relative) %>% 
  left_join(asv_annotation_blast_color_ag %>% 
              select(asv_key,color_label_group_distinct), by = "asv_key")

# the color palette (inherited from Ying, used in lots of project in our lab, the palette used in the NEJM paper Fig 2D https://www.nejm.org/doi/full/10.1056/NEJMoa1900623)

@@

>>>>

counts_data %>% 
  distinct(sampleid)
```

```{r}
dat <- counts_data %>% 
  select(asv_key:count_total, count_relative) %>% 
  left_join(asv_annotation_blast_color_ag %>% 
              select(asv_key,color_label_group_distinct), by = "asv_key")

# there are some ASVs that don't have a color with it, but can use the color for the genus level
color_group <- dat %>% 
  split(is.na(.$color_label_group_distinct))

# find the genus for these asv
get_table_from_database('asv_annotation_blast_ag')

no_color <- color_group %>% 
  pluck('TRUE') %>% 
  distinct(asv_key) %>% 
  inner_join(asv_annotation_blast_ag %>% 
               select(asv_key, genus))

# find the colors for these genera
genera_colors <- no_color %>% 
  distinct(genus) %>% 
  inner_join(asv_annotation_blast_color_ag %>% 
               distinct(genus, color_label_group_distinct))

# the full df for the no color genera
no_color_df <- no_color %>% 
  left_join(genera_colors)

no_color_df_full <- color_group %>% 
  pluck('TRUE') %>% 
  select(-color_label_group_distinct) %>% 
  left_join(no_color_df %>% 
              select(- genus))

# the question is do we go one taxa level higher or make a new color base and shades for the new asv 
```

```{r}
# the color palette (inherited from Ying, used in lots of project in our lab, the palette used in the NEJM paper Fig 2D https://www.nejm.org/doi/full/10.1056/NEJMoa1900623)

@@

```{r}
# the thing that is dividing the samples to lower and higher diversity 
# or just order samples by their diversity
div_order <- stb %>% 
  arrange(simpson_reciprocal) %>% 
  pull(sampleid)

dat$sampleid = factor(dat$sampleid,levels = div_order)

ggplot(dat,aes(sampleid, count_relative, fill = color_label_group_distinct) ) +
  geom_bar(stat = "identity", position="fill", width = 1) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90),
        axis.text.y = element_blank(),
        legend.position = "none") +
  scale_fill_manual(values = asv_color_set)
```
